Results

### 2025-06-06 notebooks/00_index.qmd
refactor: update

@@

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
# using CairoMakie
using GLMakie
using Statistics
using Dates
using PartialFunctions
using Unitful
using Beforerr: _theme_legend, easy_save
using SPEDAS.SpaceDataModel: set, extend, @set
using PSPAnisotropy
include("../src/psp_temp.jl")
include("../src/calc.jl")
include("../src/meta.jl")
using PSPAnisotropy: Wind, PSP, THEMIS

@@

```{julia}
using Discontinuity: ids_finder
tau = Second(30)
# psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
wind_events = ids_finder(Wind.B_GSE, tmin_wind, tmax_wind, tau, Wind.V_GSE, Wind.n_p)
# thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
```

@@

>>>>

## Setup

```{julia}
using Dates
using DrWatson
using PSPAnisotropy
using PSPAnisotropy: Wind, PSP, THEMIS
using Discontinuity
```

@@

```{julia}
using Speasy
using SPEDAS: ulabel, smooth, tnorm_combine, tplot
using DimensionalData
# using CairoMakie
using GLMakie
using Statistics
using PartialFunctions
using Unitful
using Beforerr: _theme_legend, easy_save
using SPEDAS.SpaceDataModel: set, extend, @set
include("../src/psp_temp.jl")
include("../src/calc.jl")
include("../src/meta.jl")

@@

```{julia}
using Discontinuity: ids_finder
tau = Second(30)
psp_events = ids_finder(PSP.B, tmin_psp, tmax_psp, tau)
wind_events = ids_finder(Wind.B_GSE, tmin_wind, tmax_wind, tau, Wind.V_GSE, Wind.n_p)
thm_events = ids_finder(THEMIS.B_FGL_GSE, tmin_wind, tmax_wind, tau)
```

@@

## Batch processing

Wind Speed, Time to Earth
300 km/s, ~5.8 days
400 km/s, ~3.9 days
500 km/s, ~3.5 days
700 km/s, ~2.5 days

### 2025-06-06 notebooks/10_results.qmd
refactor: update

```{julia}
using DrWatson
using PSPAnisotropy.Dataset: load_all
using Discontinuity: var_mapping
import Beforerr: easy_save
using GLMakie, AlgebraOfGraphics
m = var_mapping()
```

```{julia}
df_enc_7 = load_all(7);
df_enc_8 = load_all(8);
df_enc_9 = load_all(9);
df = reduce(vcat, [df_enc_7, df_enc_8, df_enc_9], cols=:intersect);
```

>>>>

```{julia}
using DrWatson
using PSPAnisotropy.Dataset: load_all
using Discontinuity: var_mapping
import Beforerr: easy_save
using GLMakie, AlgebraOfGraphics
m = var_mapping()
df = PSPAnisotropy.workload()
```
